Parallel Multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-06-15 hpmoon-hpca.tex
Modifications for blind review and format

\documentclass[Afour,sagev,times]{sagej}

@@

\runninghead{Garc\'ia-S\'anchez et al.}

\title{Parallel Multi-objective optimization using co-evolutionary islands and search space overlapping}

\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, \\Pedro Angel Castillo and Juan Juli\'an Merelo\affilnum{1}}

\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}

\corrauth{Pablo Garc\'ia-S\'anchez,
ETS. Ingenierías en Inform\'atica y Telecomunicaci\'on and CITIC-UGR,
C/Periodista Daniel Saucedo s/n,
Universidad de Granada,
18071, Granada, Spain.}

\email{pablogarcia@ugr.es}

@@

\keywords{Multi-objective algorithms, NSGA-II, Island model, distributed evolutionary algorithms}

@@

To solve this issue, some authors have proposed the usage of Master-Slave approaches. For example,  \citep{Durillo08masterslave} compared different master-slave approaches {\color{red} TODO DESCRIBIR MEJOR ESTE TRABAJO}. The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computational power {\color{red} TODO Y ESTE}.

@@

\begin{table*}
\centering
\resizebox{16cm}{!}{
\begin{tabular}{|c||c|c|c|c||c|c|c|c||c|c|c|c||}
\hline
	&	\multicolumn{4}{|c|}{HV}													&	\multicolumn{4}{|c|}{Spread}														&	\multicolumn{4}{|c|}{IGD}														\\ \hline

>>>>

%\documentclass[Afour,sagev,times]{sagej}
\documentclass[Crown,sagev,times,doublespace]{sagej}

@@

%\runninghead{Garc\'ia-S\'anchez et al.}
\runninghead{anonymous}
\title{Parallel Multi-objective optimization using co-evolutionary islands and search space overlapping}

%\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, \\Pedro Angel Castillo and Juan Juli\'an Merelo\affilnum{1}}
\author{ANONYMOUS FOR BLIND REVIEW \affilnum{1}}
\affiliation{\affilnum{1} ANONYMOUS FOR BLIND REVIEW}
%\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}

%\corrauth{Pablo Garc\'ia-S\'anchez,
%ETS. Ingenier\'ias en Inform\'atica y Telecomunicaci\'on and CITIC-UGR,
%C/Periodista Daniel Saucedo s/n,
%Universidad de Granada,
%18071, Granada, Spain.}

\corrauth{ANONYMOUS FOR BLIND REVIEW.}

%\email{pablogarcia@ugr.es}
\email{anonymous}

@@

\keywords{Multi-objective algorithms, NSGA-II, Island model, distributed evolutionary algorithms, coevolution}

@@

To solve this issue, some authors have proposed the usage of Master-Slave approaches. For example,  \citep{Durillo08masterslave} compared different master-slave approaches: synchronous generational, asynchronous generational and asynchronous steady-state, being the latter the most promising option. The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computational power.

@@

\begin{table*}
\centering
\resizebox{13cm}{!}{
\begin{tabular}{|c||c|c|c|c||c|c|c|c||c|c|c|c||}
\hline
	&	\multicolumn{4}{|c|}{HV}													&	\multicolumn{4}{|c|}{Spread}														&	\multicolumn{4}{|c|}{IGD}														\\ \hline
